Remark on the hypothetical judgment

### 2015-08-01 paper.tex
begin discussing propositional witnesses

If we are to take the explanation of the elimination rules seriously, then, we
must read Martin-L\"of as having already a kind of hypothetical judgment whose
evidence consists in any effective means at all of transforming the evidence for
the premise into the evidence for the conclusion (we might call this ``material
consequence'' as opposed to ``logical consequence''), so the use of the uniform
hypothetical judgment elsewhere has not somehow removed the need for this kind
of inference.

@@

%%% TODO:
%%% - discuss propositional witnesses
%%% - realizability as unary logical relations
%%% - (nuprl) type theory as binary logical relations
%%% - what do the propositions give us over the judgments? (witnesses, extensional identity)
%%% - harper's presentation of admissibility & derivability in pfpl
%%% - noam zeilberger's use of non-uniform hypothetical judgment

>>>>

If we are to take the explanation of the elimination rules seriously, then, we
must read Martin-L\"of as having already at his disposal a kind of hypothetical
judgment whose evidence consists in any effective means at all of transforming
the evidence for the premise into the evidence for the conclusion (we might call
this ``material consequence'' as opposed to ``logical consequence''), so the use
of the uniform hypothetical judgment elsewhere has not somehow removed the need
for this kind of inference.

@@

\section{Realizability and Type Theory}

Now that we have settled upon an explanation for hypothetical judgment, let us
return to the notion of propositions and implication, and their respective
notions of ``construction''. Like ``proof'', the term ``construction'' is also
ambiguous in that it may refer to an act of constructing, and it may also denote
a concrete mathematical object.

A construction for a judgment is simply the act of coming to know it---if it is
to be thought of as an object, it is at least a tensed, ephemeral one; this is
what Martin-L\"of calls a \emph{demonstration}. On the other hand, a
construction for a proposition is a mathematical object, not an experience: it
is the object that the subject constructs during the verification of a
proposition. This latter sort of construction is called a \emph{witness}, or,
following realizability, a \emph{realizer}.

%%% TODO:
%%% - realizability as unary logical relations
%%% - (nuprl) type theory as binary logical relations
%%% - what do the propositions give us over the judgments? (witnesses, extensional identity)
%%% - harper's presentation of admissibility & derivability in pfpl
%%% - noam zeilberger's use of non-uniform hypothetical judgment
